Inspection of additive manufacturing from a single x-ray projection using local empirical null hypotheses

### 2019-06-20 reports/paper1/paper.tex
Paper revise

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[square,semicolon]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}
\usepackage{MnSymbol} %udots
\usepackage{afterpage} %\afterpage{\clearpage}
\usepackage{siunitx} %for measurements
\usepackage[figurename=Fig.]{caption}
\usepackage[numbib]{tocbibind} %number references and figure title
\usepackage{authblk}

@@

\title{Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection}
\author[1, *]{S.E.~Lo}
\author[2]{J.W.~Warnett}
\author[2]{G.J.~Gibbons}
\author[2]{M.A.~Williams}
\author[3]{T.E.~Nichols}
\author[1]{J.A.~Brettschneider}
\affil[1]{Department of Statistics, University of Warwick, Coventry, CV4 7AL, UK}
\affil[2]{Warwick Manufacturing Group, University of Warwick, Coventry, CV4 7AL, UK}
\affil[3]{Big Data Institute, Old Road Campus, University of Oxford, Oxford, OX3 7LF, UK}
\affil[*]{Corresponding author: s.ip@warwick.ac.uk, +442476574812}

@@

\begin{abstract}
\noindent
\textbf{BACKGROUND}: X-ray computed tomography can be used for defect detection in additive manufacturing (AM). Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features.
\newline
\textbf{OBJECTIVE}: It was investigated whenever it is possible to detect defects based on a single angular projection. The motivation behind it is that defect detection in projection space should be faster than in reconstruction space.
\newline
\textbf{METHODS}: An AM sample was manufactured with voids to see if they can be detected. The x-ray projection was compared with a simulation of that projection under the face of uncertainty by treating each pixel as a hypothesis test. The simulation was not perfect which led to misleading results. The empirical null filter was used to cater for the model misspecification so that sensible inference was achieved.
\newline
\textbf{RESULTS}: Voids with diameters in the order of millimetres were detectable. Simulation studies have shown that statistical properties such as the false discovery rate were preserved when using the filter.
\newline
\textbf{CONCLUSIONS}: Defect detection in projection space is possible. This can be extended to multiple independent projections in real time on a conveyor belt. The main bottle neck is the multiple evaluation of functions required for robust estimation in the empirical null filter. Speed up could be possible by implementing the filter on a GPU or exploring further robust estimators.
\newline
\newline
\emph{Keywords:} Hypothesis testing, local normalisation, image filtering, projection space, additive manufacturing, voids, defects, quality control
\end{abstract}

@@

This paper investigates whether defects can be detected from a single x-ray projection. To validate our method, we designed an AM test cuboid with purposely designed voids. An x-ray projection was obtained and compared with the simulation from \emph{aRTist} in order to detect these voids. The simulation was not perfect which led to misleading results. The empirical null filter was used to cater for the model misspecification so that sensible inference was achieved. The apparatus and procedures are shown in the methods section. In addition, computational implementation and simulation studies of the empirical null filter are discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

\subsection{Apparatus and Data Collection}

An ABS plastic test cuboid (\SI{40}{\milli\metre} $\times$ \SI{40}{\milli\metre} $\times$ \SI{60}{\milli\metre}) with voids was purposefully manufactured to see if they can be detected. The CAD model of the test cuboid is shown in Fig.~\ref{fig:inference_testObject}. It was manufactured using a \emph{Fortus 400mc (Stratasys, US)} 3D printer. Six voids of each diameter, \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}, were designed in the CAD model. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, the other ones were arranged irregularly. The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$ \citep{hanseen2013fortus}.

@@

\subsection{Statistical Methodology}

A method was proposed to compare a single projection with a simulation of that projection and treating it as the ground truth. This was done by using two-tailed multiple hypothesis testing \citep{fisher1970statistical, neyman1933on, pearson1900on} controlling the false discovery rate (FDR) \citep{benjamini2010discovering, benjamini1995controlling}, treating each pixel as an individual test. A disagreement too big will classify that pixel as a positive result. Beforehand, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics. This was necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.

A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic, together makes a $z$ image, is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection.

The variance model, $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}. The fitting of the model was done using the held out replicated projections of the sample. These replicated projections were manually segmented. This provided variance-mean data, where each pixel is a data point, and was used to fit the variance model. The model used was a gamma distributed generalised linear model \citep{mccullagh1984generalized, nelder1972generalized} with an identity link. The variance was predicted using the grey value in the simulated projection as the predictor variable when working out the test statistics.

It was assumed that the grey values were Normal, therefore the test statistics should be approximately Normal as well. Let the test statistic of the pixel at position $(x,y)$ be
\begin{equation}
Z_{x,y}\sim\normal(\mu_{x,y},\widehat{\sigma}_{0,x,y}^2)
\end{equation}
for $x=1,2,\cdots,W$ and $y=1,2,\cdots,H$. $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$ respectively. Their estimates are $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ also respectively. Define the null hypotheses to be
\begin{equation}
  H_{0,x,y}:\mu_{x,y}=\widehat{\mu}_{0,x,y}
\end{equation}
which are tested against
\begin{equation}
  H_{1,x,y}:\mu_{x,y}\neq\widehat{\mu}_{0,x,y} \ .
\end{equation}
The empirical null filter aims to obtain the estimators $\widehat{\mu}
_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ for all $x$ and $y$. This is based on the empirical null \citep{efron2004large} where hypothesis testing is done by comparing a test statistic with the empirical distribution of the majority of the test statistics rather than a specified null distribution.

To obtain the estimates, a circular kernel with radius $r$ was centred at $(x,y)$. All the pixels captured by the circular kernel and the region of interest (ROI) were pooled together to obtain a kernel density estimate \citep{friedman2001elements, parzen1962on}
\begin{equation}
\widehat{p}_{Z_{x,y}}(z) = 
\frac{1}{nh}
  \sum_{i,j\in K_{x,y}}\phi\left(
    \dfrac{z_{i,j}-z}{h}
  \right)
\end{equation}
where $K_{x,y} = \text{kernel centred at }(x,y) \cap \text{ROI}$, $n$ is the number of pixels captured by $K_{x,y}$, $\phi(z)$ is the probability density function of a standard Normal random variable and $h$ is the bandwidth. The bandwidth was chosen such that
\begin{equation}
  h = (0.9n^{-1/5}\ + 0.16) \times \text{min}\left(s_{x,y},\text{IQR}_{x,y}/1.34\right)
  \label{eq:inference_ourruleofthumb}
\end{equation}
where $s_{x,y}$ and $\text{IQR}_{x,y}$ are the sample standard deviation and sample interquartile range of the test statistics in $K_{x,y}$, similar to Silverman's rule of thumb \citep{sheather2004density, silverman1986density}. The estimates were obtained by solving
\begin{equation}
\widehat\mu_{0,x,y} = \text{argmax} \widehat{p}_{Z_{x,y}}(z)
\end{equation}
using the Newton-Raphson method and
\begin{equation}
  \widehat{\sigma}_{0,x,y} = \left[
    \left.
      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}_{Z_{x,y}}(z)
    \right|_{z=\widehat{\mu}_{0,x,y}}
  \right]^{-1/2}
\end{equation}
\citep{efron2004large}. The test statistics were normalised using
\begin{equation}
  T_{x,y} = 
  \dfrac{
    Z_{x,y}-\widehat{\mu}_{0,x,y}
  }
  {
    \widehat{\sigma}_{0,x,y}
  } \ .
\end{equation}
All the normalised test statistics were converted to $p$-values
\begin{equation}
  p_{x,y} = 2(1-\Phi(|t_{x,y}|))
\end{equation}
and was used in the  Benjamini-Hochberg \citep{benjamini1995controlling}(BH) procedure at the 5\% FDR level to classify pixels as positive or not for defects.

@@

The empirical null filter was implemented using \emph{ImageJ} \citep{abramoff2004image, perez2013image, schindelin2012fiji, schneider2012nih} by modifying the existing class \texttt{RankFilters}. It contains implementations of filters, such as the mean filter and median filter, using a circular kernel and multiple threads. Each thread filters a row in parallel.

@@

When filtering a pixel, the Newton-Raphson method was used to solve for $\widehat{\mu}_{0,x,y}=z$
\begin{equation}
  \dfrac{\partial}{\partial z}\ln\widehat{p}_{Z_{x,y}}(z) = 0
\end{equation}
by using the iterative procedure
\begin{equation}
  z^{(r+1)} =
  z^{(r)}
  -\dfrac{
    \left.
      \dfrac{
        \partial
      }
      {
        \partial z
      }
      \ln\widehat{p}_{Z_{x,y}}(z)
    \right|_{z = z^{(r)}}
  }
  {
    \left.
      \dfrac{
        \partial^2
      }
      {
        \partial z^2
      }
      \ln\widehat{p}_{Z_{x,y}}(z)
    \right|_{z = z^{(r)}}
  } 
\end{equation}
where $z^{(0)}$ is the initial value. A convergence criteria was met when either 10 update steps were taken or when
\begin{equation}
  \log\left[\left|
    \left.
    \dfrac{
      \partial
    }
    {
      \partial z
    }
  \ln\widehat{p}_{x,y}(z)
  \right|_{z=z^{(r)}}
  \right|\right]
  <-5
\end{equation}
at the current step. This was chosen arbitrary to speed up the algorithm without losing too much accuracy. The solution is valid if
\begin{equation}
  \left.
    \dfrac{
      \partial^2
    }
    {
      \partial z^2
    }
    \ln\widehat{p}_{Z_{x,y}}(z)
  \right|_{z=\widehat{\mu}_{0,x,y}}
  < 0 \ .
\end{equation}
Further initial values were generated by sampling from $\normal(z^{(0)}, s_{x,y}^2)$. This was done multiple times until 3 valid solutions were obtained. The best solution, the one with the largest $\ln\widehat{p}_{Z_{x,y}}\left(\widehat{\mu}_{0,x,y}\right)$, out of all the different initial values was used as the final answer.

\subsection{Simulation}

The empirical null filter was tested to see if it can detect simulated defects from a $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated image. A defect is a pixel which has a value not distributed under the null distribution, but instead an alternative distribution. For example suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect would have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$. A $\SI{30}{\pixel}\times \SI{30}{\pixel}$ square defect was simulated. A kernel can capture the entire defect if its radius is large enough.

Contamination is the result of a linear transform of the test statistics $Z_{x,y}$. For example in this experiment, the image was multiplied by 2 and a gradient was added to it. Suppose the image does contain defects, then an example of a resulting distribution is
\begin{align}
  Z_{x,y}|H_{0,x,y}&\sim\normal(\mu_{0,x,y},2^2)
  \\
  Z_{x,y}|H_{1,x,y}&\sim\normal(2\mu_1+\mu_{0,x,y},2^2)
\end{align}
where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. This was used in this study to simulate a contaminated image with defects. The contaminated square defected image is shown in Fig.~\ref{fig:inference_defectSquare2Example}.

The contamination is a nuisance because the test statistics will have larger variance and larger values at the two corners. This will cause an inflation in false positives which will lead to incorrect inference.

@@

The receiver operating characteristic (ROC) curve \citep{cook2007use, friedman2001elements, green1966signal, hanley1982meaning, metz1978basic} was studied in this experiment. The ROC is a parametric plot, plotting the true positive rate (sensitivity) against the false positive rate ($1-\text{specificity}$) for varying thresholds. The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}. Interpretations of the area do exist \citep{hanley1982meaning, metz1978basic} and discussed thoroughly \citep{cook2007use}.

A simulation study was conducted where the contaminated defected image was filtered for various kernel radiuses for $\mu_1=3$. Hypothesis testing was done on the uncontaminated defected image and filtered contaminated defected image. The area under the ROC curve and various errors were recorded. This was repeated 100 times by simulating another image. To form a baseline to compare with, the results of the uncontaminated image were all pooled together to obtain the empirical distribution of the ROC area and errors without contamination.

@@

For good results, the faces of the AM cuboid were segmented. This was necessary because the empirical null filter assumes that the null parameters varied spatially smoothly and slowly. Manual segmentation was easy to do because a cuboid has 6 faces. However, segmentation of faces cannot be generalised well to AM samples with complicated geometry and curved surfaces.

@@

\setlofname{Figure Captions}
\listoffigures

\section{Figures}

\begin{figure}
  \centering
  \includegraphics[width=0.35\textwidth]{../figures/inference/TestObject.png}
  \caption{The CAD model of the test cuboid with voids. Six voids of each diameter, \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}, were designed in the CAD model. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, the other ones were arranged irregularly. The scale shown is approximate.}
  \label{fig:inference_testObject}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
  \caption{A $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated Gaussian image with a $\SI{30}{\pixel} \times \SI{30}{\pixel}$ square defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(6+\mu_{0,x,y},2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.}
  \label{fig:inference_defectSquare2Example}
\end{figure}

>>>>

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[square,comma]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}
\usepackage{MnSymbol} %udots
\usepackage{afterpage} %\afterpage{\clearpage}
\usepackage{siunitx} %for measurements
\usepackage[figurename=Fig.]{caption}
\usepackage[numbib]{tocbibind} %number references and figure title
\usepackage{authblk}

@@

\title{Inspection of additive manufacturing from a single x-ray projection using local empirical null hypotheses}
\date{2019}
\author[1]{S.E.~Lo}
\author[2]{J.W.~Warnett}
\author[2]{G.J.~Gibbons}
\author[2]{M.A.~Williams}
\author[3]{T.E.~Nichols}
\author[1,*]{J.A.~Brettschneider}
\affil[1]{Department of Statistics, University of Warwick, Coventry, CV4 7AL, UK}
\affil[2]{Warwick Manufacturing Group, University of Warwick, Coventry, CV4 7AL, UK}
\affil[3]{Big Data Institute, Old Road Campus, University of Oxford, Oxford, OX3 7LF, UK}
\affil[*]{Corresponding author: julia.brettschneider@warwick.ac.uk, +442476574812}

@@

\begin{abstract}
\noindent
\textbf{BACKGROUND}: X-ray computed tomography can be used for defect detection in additive manufacturing (AM). Typically, x-ray projections of an object are taken at a number of angles that are then reconstructed to create a 3D representation of the object inclusive of internal features.
\newline
\textbf{OBJECTIVE}: It was investigated whether it is possible to detect defects based on a single angular projection, avoiding the time-consuming reconstruction process.
\newline
\textbf{METHODS}: An AM sample was manufactured with voids to see if they can be detected. The x-ray projection was compared with a simulation of that projection under the face of uncertainty by treating each pixel as a hypothesis test. To overcome imperfections of the simulation, the empirical null filter was used to cater for the model misspecification so that sensible inference was achieved.
\newline
\textbf{RESULTS}: Voids with diameters in the order of millimetres were detectable. Simulation studies have shown that statistical properties such as the false discovery rate were preserved.
\newline
\textbf{CONCLUSIONS}: Defect detection in projection space is possible. This work is a contribution towards real-time quality control in AM. The main bottle neck is the multiple evaluation of functions required for robust estimation in the empirical null filter. Speeding up could be possible by implementing the filter on a GPU or exploring further robust estimators.
\newline
\newline
\emph{Keywords:} Additive manufacturing, projection space, hypothesis testing, empirical null, local normalisation, image filtering, voids, defects, quality control
\end{abstract}

@@

This paper investigates whether defects can be detected from a single x-ray projection. To validate our method, we designed an AM test sample with purposely designed voids. An x-ray projection was obtained and compared with the simulation from \emph{aRTist} in order to detect these voids. The simulation was not perfect which led to misleading results. The empirical null filter was used to cater for the model misspecification so that sensible inference was achieved. The apparatus and procedures are shown in the methods section. In addition, computational implementation and simulation studies of the empirical null filter are discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

\subsection{Apparatus and Data Collection}
\label{subsection:appratus}

An ABS plastic cuboid (\SI{40}{\milli\metre} $\times$ \SI{40}{\milli\metre} $\times$ \SI{60}{\milli\metre}) with voids was purposefully manufactured to see if they can be detected. The CAD model of the test sample is shown in Fig.~\ref{fig:inference_testObject}. It was manufactured using a \emph{Fortus 400mc (Stratasys, US)} 3D printer. Six voids of each diameter, \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}, were designed in the CAD model. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, the other ones were arranged irregularly. The precision of the manufacturing was in the order of $\pm\SI{0.1}{\milli\metre}$ \citep{hanseen2013fortus}.

@@

\subsection{The Empirical Null Filter}

We propose a statistical method to compare a single projection with a simulation of that projection to look for any significant differences which may indicate a defect. It is built on two-tailed multiple hypothesis testing \citep{fisher1970statistical, neyman1933on, pearson1900on} controlling the false discovery rate (FDR) \citep{benjamini2010discovering, benjamini1995controlling}, conducting individual test for each pixel. A disagreement too big, relative to the anticipated variance of the projection, will classify that pixel as a positive result. Beforehand, the empirical null \citep{efron2004large} is used to locally normalisation \citep{sage2018local, sage2003teaching} the test statistics. This is necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.

Fig.~\ref{fig:flowchart} shows a flowchart which summarises the process of the experiment. The CAD model was used as a blueprint for the manufacture of the test sample. Projections of the test sample and the simulated projection were obtained and compared under the face of uncertainty. The test statistics from the comparison were filtered using the empirical null filter and converted to $p$-values. A threshold was used for the $p$-values to classify pixels as positive for defects or not.

For each position $(x,y)$, we calculate a test statistic
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection. We used a variance model $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ with linear relationship between the variance and the grey value \citep{yang2010noise}. We used was a gamma distributed generalised linear model \citep{mccullagh1984generalized, nelder1972generalized} with an identity link. The fitting of the model was done using the held out replicated projections of the sample (see Section \ref{subsection:appratus}). These replicated projections were manually segmented so that only pixels which represent the test sample were used. This provided variance-mean data, where each pixel is a data point, which was used to fit the variance model. The variance was predicted using the grey value in the simulated projection as the predictor variable.

It was assumed that the grey values were Normally distributed, therefore the test statistics should be approximately Normal as well. Let the test statistic of the pixel at position $(x,y)$ be
\begin{equation}
Z_{x,y}\sim\normal(\mu_{x,y},\widehat{\sigma}_{0,x,y}^2)
\end{equation}
for $x=1,2,\cdots,W$ and $y=1,2,\cdots,H$. $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$ respectively with estimates are $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ respectively. Define the null hypotheses
\begin{equation}
  H_{0,x,y}:\mu_{x,y}=\widehat{\mu}_{0,x,y}
\end{equation}
and the alternative hypotheses
\begin{equation}
  H_{1,x,y}:\mu_{x,y}\neq\widehat{\mu}_{0,x,y} \ .
\end{equation}
The empirical null filter aims to obtain the estimators $\widehat{\mu}
_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ for all $x$ and $y$. This is based on the empirical null \citep{efron2004large} where hypothesis testing is done by comparing a test statistic with the empirical distribution of the majority of the test statistics rather than a specified null distribution.

To obtain the estimates, a circular kernel $C_r(x,y)$ with radius $r$ was centred at $(x,y)$. All the pixels captured by the circular kernel and the region of interest (ROI) were pooled together to obtain a kernel density estimate \citep{friedman2001elements, parzen1962on}
\begin{equation}
\widehat{p}_{Z_{x,y}}(z) = 
\frac{1}{nh}
  \sum_{i,j\in K_{x,y}}\phi\left(
    \dfrac{z_{i,j}-z}{h}
  \right)
\end{equation}
where $K_{x,y} = C_r(x,y) \cap \text{ROI}$, $n$ is the number of pixels captured by $K_{x,y}$, $\phi(z)$ is the probability density function of a standard Normal random variable and $h$ is the bandwidth. The bandwidth was chosen such that
\begin{equation}
  h = (0.9n^{-1/5}\ + 0.16) \times \text{min}\left(s_{x,y},\text{IQR}_{x,y}/1.34\right)
  \label{eq:inference_ourruleofthumb}
\end{equation}
where $s_{x,y}$ and $\text{IQR}_{x,y}$ are the sample standard deviation and sample interquartile range of the test statistics in $K_{x,y}$, similar to Silverman's rule of thumb \citep{sheather2004density, silverman1986density}. The estimates were obtained by solving
\begin{equation}
\widehat\mu_{0,x,y} = \argmax\widehat{p}_{Z_{x,y}}(z)
\end{equation}
using the Newton-Raphson method and
\begin{equation}
  \widehat{\sigma}_{0,x,y} = \left[
    \left.
      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}_{Z_{x,y}}(z)
    \right|_{z=\widehat{\mu}_{0,x,y}}
  \right]^{-1/2}
\end{equation}
\citep{efron2004large}. The test statistics were normalised using
\begin{equation}
  T_{x,y} = 
  \dfrac{
    Z_{x,y}-\widehat{\mu}_{0,x,y}
  }
  {
    \widehat{\sigma}_{0,x,y}
  }
\end{equation}
and converted to $p$-values
\begin{equation}
  p_{x,y} = 2(1-\Phi(|t_{x,y}|)) \ .
\end{equation}

Pixels are classified as positive for defects if its $p$-value is less than some threshold $\alpha$. The Benjamini-Hochberg \citep{benjamini1995controlling}(BH) procedure was used to select the threshold such that the FDR is less than 5\%. This was done by ordering the $p$-values such that $p_{(1)}\leqslant p_{(2)}\leqslant \cdots \leqslant p_{(N)}$, where $N$ is the area of the ROI, and using the threshold
\begin{equation}
  \alpha = \frac{0.05 k}{N}
\end{equation}
where
\begin{equation}
  k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{N}\alpha
  \ .
\end{equation}

@@

The empirical null filter was implemented using \emph{ImageJ} \citep{abramoff2004image, perez2013image, schindelin2012fiji, schneider2012nih} by modifying the existing class \texttt{RankFilters}. The class contains implementations of filters, such as the mean filter and the median filter, using a circular kernel and multiple threads. Each thread filters a row in parallel.

@@

When filtering a pixel, the Newton-Raphson method was used to solve for $\widehat{\mu}_{0,x,y}=z$
\begin{equation}
  \dfrac{\partial}{\partial z}\ln\widehat{p}_{Z_{x,y}}(z) = 0
\end{equation}
by using the iterative procedure
\begin{equation}
  z^{(r+1)} =
  z^{(r)}
  -\dfrac{
    \left.
      \dfrac{
        \partial
      }
      {
        \partial z
      }
      \ln\widehat{p}_{Z_{x,y}}(z)
    \right|_{z = z^{(r)}}
  }
  {
    \left.
      \dfrac{
        \partial^2
      }
      {
        \partial z^2
      }
      \ln\widehat{p}_{Z_{x,y}}(z)
    \right|_{z = z^{(r)}}
  } 
\end{equation}
where $z^{(0)}$ is the initial value. A convergence criteria was met when either 10 update steps were taken or when
\begin{equation}
  \log\left[\left|
    \left.
    \dfrac{
      \partial
    }
    {
      \partial z
    }
  \ln\widehat{p}_{x,y}(z)
  \right|_{z=z^{(r)}}
  \right|\right]
  <-5
\end{equation}
at the current step. This was chosen arbitrary to speed up the algorithm without losing too much accuracy. The solution is valid if
\begin{equation}
  \left.
    \dfrac{
      \partial^2
    }
    {
      \partial z^2
    }
    \ln\widehat{p}_{Z_{x,y}}(z)
  \right|_{z=\widehat{\mu}_{0,x,y}}
  < 0 \ .
\end{equation}
Further initial values were generated by sampling from $\normal(z^{(0)}, s_{x,y}^2)$. This was done multiple times until 3 valid solutions were obtained. The best solution, the one with the largest $\ln\widehat{p}_{Z_{x,y}}\left(\widehat{\mu}_{0,x,y}\right)$ out of all the different initial values, was used as the final answer.

\subsection{Simulation of Defect Detection}

We tested if the empirical null filter can detect simulated defects from a $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated image. Statistically speaking, a defect is a pixel which has a value not distributed under the null distribution, but instead a alternative distribution. For example suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect would have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$. A $\SI{30}{\pixel}\times \SI{30}{\pixel}$ square defect was simulated. A kernel can capture the entire defect if its radius is large enough.

Contamination was simulated by a linear transform of the test statistics $Z_{x,y}$. For example in this experiment, the image was multiplied by 2 and a gradient was added. The null and alternative distributions are
\begin{align}
  Z_{x,y}|H_{0,x,y}&\sim\normal(\mu_{0,x,y},2^2)
  \\
  Z_{x,y}|H_{1,x,y}&\sim\normal(\mu_{0,x,y}+2\mu_1,2^2)
\end{align}
respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. A simulated contaminated defected image was made by sampling $Z_{x,y}|H_{0,x,y}$ in areas with no defects and $Z_{x,y}|H_{1,x,y}$ with defects. An example of contaminated square defected image is shown in Fig.~\ref{fig:inference_defectSquare2Example}.

The contamination will cause the test statistics to have larger variance and larger values at the two corners where $\mu_{0,x,y}$ is large. This will cause an inflation in false positives.

@@

The receiver operating characteristic (ROC) curve \citep{cook2007use, friedman2001elements, green1966signal, hanley1982meaning, metz1978basic} is a parametric plot, displaying the true positive rate (sensitivity) against the false positive rate ($1-\text{specificity}$) for varying thresholds. The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}. Interpretations of the area do exist \citep{hanley1982meaning, metz1978basic} and discussed thoroughly \citep{cook2007use}.

A simulation study was conducted where a simulated contaminated defected image was filtered for various kernel radiuses for $\mu_1=3$. Hypothesis testing was done on the uncontaminated defected image and filtered contaminated defected image. The area under the ROC curve and various errors were recorded. This was repeated 100 times by simulating another image. To form a baseline to compare with, the results of the uncontaminated image were all pooled together to obtain the empirical distribution of the ROC area and errors without contamination.

@@

For good results, the faces of the AM sample were segmented. This was necessary because the empirical null filter assumes that the null parameters varied spatially smoothly and slowly. Manual segmentation was easy to do because a cuboid has 6 faces. However, segmentation of faces cannot be generalised well to AM samples with complicated geometry and curved surfaces.

@@

\setlofname{Figure Captions}
\listoffigures
\clearpage
\section{Figures}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.49\textwidth]{../figures/inference/TestObject.png}
  \caption{The CAD model of the test sample with voids. Six voids of each diameter, \SI{2.4}{\milli\metre}, \SI{1.2}{\milli\metre}, \SI{0.6}{\milli\metre} and \SI{0.3}{\milli\metre}, were designed in the CAD model. Voids with diameters \SI{2.4}{\milli\metre} and \SI{0.6}{\milli\metre} were regularly arranged, the other ones were arranged irregularly. The scale shown is approximate.}
  \label{fig:inference_testObject}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/flowchart.eps}
  \caption{Flowchart showing the process of obtaining and comparing a projection of the test sample with the simulated projection.}
  \label{fig:flowchart}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{../figures/inference/defectSquare2Example_imageContaminated.eps}
  \caption{A $\SI{256}{\pixel}\times \SI{256}{\pixel}$ contaminated Gaussian image with a $\SI{30}{\pixel} \times \SI{30}{\pixel}$ square defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{0,x,y}+6,2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image.}
  \label{fig:inference_defectSquare2Example}
\end{figure}

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_roc.eps}
        \caption{ROC area}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type1.eps}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectRadiusSquare_fdr.eps}
        \caption{FDR}
      \end{subfigure}
    }
  \caption{ROC area and various errors obtained when conducting a hypothesis test on a $\SI{256}{\pixel} \times \SI{256}{\pixel}$ filtered contaminated Gaussian image with a $\SI{30}{\pixel}\times \SI{30}{\pixel}$ square defect. Various kernel radiuses were investigated. The dashed lines show the resulting 95\% empirical confidence interval when the hypothesis test was done on the uncontaminated image with a defect. The null and alternative distributions are $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},2^2)$ and $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{0,x,y}+6,2^2)$ respectively where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. The test was done at the 5\% FDR level. The box plot summarise the 100 repeated measurements of the experiment.}
  \label{fig:inference_Experiment_DefectRadiusSquare}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{../figures/inference/segment.JPG}
  \caption{The x-ray projection was segmented further into 7 segments or ROI.}
  \label{fig:inference_segmentFurther}
\end{figure}
